---
title: "Assingment NYC Flight Data"
author: "Ankit Raheja"
date: "October 11, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## NYC Flight Data

Your job is to create a "rectangular" table useful for modeling from flight data. In the folder `02-fundamentals/data` there are four CSV files: `flights.csv`, `airports.csv`, `planes.csv` and `weather.csv`.  Put code in each of the sections provided.

## 1. Read Data

Using the `readr` package read the `flights` data.

```{r}
flights<-readr::read_csv("C:/Users/araheja/CSX460/02-fundamentals/data/flights.csv")
airports<-readr::read_csv("C:/Users/araheja/CSX460/02-fundamentals/data/airports.csv")
weather<-readr::read_csv("C:/Users/araheja/CSX460/02-fundamentals/data/weather.csv")
planes<-readr::read_csv("C:/Users/araheja/CSX460/02-fundamentals/data/planes.csv")

```

## Numeric Variables  

Plot a histogram of arrival delays and departure delays 

```{r}
hist(flights$arr_delay,main = "Arrival Delay Histogram",xlab = "delay")
hist(flights$dep_delay,main = "Departure Delay Histogram",xlab = "delay")

```

## Scatterplot

Plot a scatterplot of date vs arrival delay 

```{r}
plot(as.Date(flights$time_hour),flights$arr_delay,main = "scatterplot of date vs arrival delay",xlab = "Date",ylab = "Time")
```



## Create tables for Categorical Variables

Create a `table` of occurences of origin airports and carrier.

```{r}
table(flights$origin,flights$carrier)

```


## Join Data

**Read** in the other data sets. Use methods to join the data together to create a single table containing one record per row.  (HINT: see `?data.table` or `?dplyr::join`)

```{r}
library(dplyr)
left_join(x=flights,y=airports,by = c("origin"="faa"))%>%left_join(.,y=airports,by = c("dest"="faa"))%>%left_join(.,y=planes,by = c("tailnum"="tailnum"))%>%left_join(.,y=weather,by = c("month", "day", "origin", "hour"))

```



